---
title: "Weather_Data"
author: "Matthew Yi"
date: "2023-07-19"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Setup chunk - run this to load the data.

Set working directory, install packages, load packages, load data, lubridate.
Data is missing for October 31st at 23:55:00 so insert data at that time equal to the previous reading.

```{r}
rm(list=ls())
setwd(dir = "C:/Users/yclma/OneDrive/Documents/2023 S2/COSC345/COSC345-Game/data")
library("readxl") 
library(dplyr)
library(lubridate)
weather = read_xlsx("C:/Users/yclma/OneDrive/Documents/2023 S2/COSC345/COSC345-Game/data/Weather_Data.xlsx")
weather$DATE <- ymd(weather$DATE)
weather$TIME <- sub("^[^ ]+ ", "", weather$TIME)
weather$TIME <- ifelse(weather$TIME == "1899-12-31", "00:00:00", weather$TIME)
# weather$TIME <- as_datetime(weather$TIME, format = "%H:%M:%S")
weather$TIME <- hms(weather$TIME)
# identify missing data
# for (i in 2:length(weather$TIME)) {
#   if (!((weather$TIME[i] - weather$TIME[i - 1]) %in% c("5M 0S", "-23H -55M 0S", "1H -55M 0S"))) {
#     print(i)
#   }
# }
# weather <- rbind(weather[1:35422, ], weather[35423,], weather[35423:nrow(weather), ])
# weather$TIME[35424] = hms("23H 55M 0S")
weather <- rbind(weather[1:44063, ], weather[44064,], weather[44064:nrow(weather), ])

weather$DATE[44064] = ymd("2022-10-31")
weather$TIME[44064] = hms("23H 55M 0S")
weather$TEMP[44064] = 12.8
weather$RH[44064] = 74
weather$WINDSPD[44064] = 1.1
weather$WINDIR[44064] = 20
weather$GLOBAL[44064] = 0.8
weather$UVA[44064] = 0.0
weather$UVB[44064] = 0.01
weather$VISIBLE[44064] = 0
weather$RAIN[44064] = 0
weather$PRESS[44064] = 1002
weather$MAXGUST[44064] = 1.8
weather$GUSTIME[44064] = 2350
```

Segment the data into 28 segments. Seasons are one week long.

```{r}
library(dplyr)
library(lubridate)

sub_weather <- list()

start_date <- ymd("2022-06-01")
end_date <- ymd("2023-05-31")
date_intervals <- seq(start_date, end_date, by = "13 days")

for (i in 1:(length(date_intervals) - 1)) {
  interval_start <- date_intervals[i]
  interval_end <- date_intervals[i + 1] - days(1)
  subset <- weather %>% filter(DATE >= interval_start, DATE <= interval_end)
  sub_weather[[i]] <- subset
}
```

Generate 10 years of random data

```{r}
weather2 <- data.frame()

for (i in 1:10) {
    for (i in 1:28) {
    start_date <- min(sub_weather[[i]]$DATE)
    end_date <- max(sub_weather[[i]]$DATE)
    dates <- seq(start_date, end_date, by = "1 days")
  
    chosen_days <- sample(x = dates, size = 1, replace = FALSE)
    
    week <- sub_weather[[i]] %>% 
      filter(DATE %in% chosen_days) # this filters in order so even if chosen_days is not sorted week will be
    weather2 <- rbind(weather2, week)
  }
}

print(all(diff(weather2$DATE) >= 0))
print(unique(weather2$DATE))
```
Blend between days

```{r}
weather2$TIME[1] - weather2$TIME[10]
times <- weather2$TIME[253:325]

for (i in 1:(length(unique(weather2$DATE)) - 1)) {
  nine_idx <- (i * 288) - 35
  three_idx <- (i * 288) + 37
  # transitional_period <- weather2[(i*288-35):(i*288+37)]
  if (nine_idx >= 1 && three_idx <= nrow(weather2)) {
    
    for (col in colnames(weather2)) {
      if (col %in% c("DATE", "TIME")) {
        next
      }
      weather2[[col]][(i*288-35):(i*288+37)] <- round(seq(from = weather2[[col]][i*288-35], to = weather2[[col]][i*288+37], length.out = 73), (nchar(as.character(weather2[[col]][1] - floor(weather2[[col]][1])))-2))
    }  
  }
}

plot(weather2$TEMP, pch = 20)
```

Add season and day of week

```{r}
day <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
day <- rep(day, each = 288)
day <- rep(day, times = 40)

season <- c("winter", "spring", "summer", "autumn")
season <- rep(season, each = 2016)
season <- rep(season, times = 10)

weather2 <- weather2 %>% 
  mutate(day = day, season = season)

weather2 <- weather2 %>% 
  select(day, season, everything(), DATE)

weather2 <- weather2 %>% 
  rename(source_date = DATE)

colnames(weather2) <- tolower(colnames(weather2))
```


Output data to csv

```{r}
write.csv(weather2, file="weather_10yrs.csv")
```


Rain data. It rains 3.076% of the time. Most of the time it only rains for 5 mins

```{r}
rain <- data.frame(date=weather$DATE, time=weather$TIME, rain=ifelse(weather$RAIN == 0, 0, 1))
plot(rain$date, rain$rain, pch=16)
summary(rain)

rain_duration <- c()
mins_rain <- 0

for (i in 1:length(rain$date)) {
  if (rain$rain[i] == 1) {
    mins_rain <- mins_rain + 5
  } else {
    if (mins_rain != 0) {
      rain_duration <- c(rain_duration, mins_rain)
      mins_rain <- 0
    }
  }
}

rain_duration
hist(rain_duration)
summary(rain_duration)
```