---
title: "Weather_Data"
author: "Matthew Yi"
date: "2023-07-19"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Setup chunk - run this to load the data.

Set working directory, install packages, load packages, load data, lubridate.
Data is missing for October 31st at 23:55:00 so insert data at that time equal to the previous reading.

```{r}
setwd(dir = "C:/Users/yclma/OneDrive/Documents/2023 S2/COSC345/Data")
library("readxl") 
library(dplyr)
library(lubridate)
weather = read_xlsx("C:/Users/yclma/OneDrive/Documents/2023 S2/COSC345/Data/Weather_Data.xlsx")
weather$DATE <- ymd(weather$DATE)
weather$TIME <- sub("^[^ ]+ ", "", weather$TIME)
weather$TIME <- ifelse(weather$TIME == "1899-12-31", "00:00:00", weather$TIME)
# weather$TIME <- as_datetime(weather$TIME, format = "%H:%M:%S")
weather$TIME <- hms(weather$TIME)
# for (i in 2:length(weather$TIME)) {
#   if (!((weather$TIME[i] - weather$TIME[i - 1]) %in% c("5M 0S", "-23H -55M 0S", "1H -55M 0S"))) {
#     print(i)
#   }
# }
weather <- rbind(weather[1:35422, ], weather[35423,], weather[35423:nrow(weather), ])
weather$TIME[35424] = hms("23H 55M 0S")
```

Segment the data into 28 segments. For each game day, choose a random day from the corresponding 28th of the year

```{r}
library(dplyr)
library(lubridate)

sub_weather <- list()

start_date <- ymd("2022-07-01")
end_date <- ymd("2023-06-30")
date_intervals <- seq(start_date, end_date, by = "13 days")

for (i in 1:(length(date_intervals) - 1)) {
  interval_start <- date_intervals[i]
  interval_end <- date_intervals[i + 1] - days(1)
  subset <- weather %>% filter(DATE >= interval_start, DATE <= interval_end)
  sub_weather[[i]] <- subset
}

summer <- sub_weather[1:7]
```


```{r}
sub_weather <- list()

start_date <- ymd("2022-01-01")
end_date <- ymd("2022-12-31")
date_intervals <- seq(start_date, end_date, by = "13 days")
date_intervals <- c(date_intervals, end_date + days(1))  # Include the end date in the intervals

for (i in 1:28) {
  subset <- weather[weather$DATE >= date_intervals[i] & weather$DATE < date_intervals[i + 1], ]
  sub_weather[[i]] <- subset
}
summary(sub_weather[[2]])
```


Rain data. It rains 3.076% of the time. Most of the time it only rains for 5 mins
```{r}
rain <- data.frame(date=weather$DATE, time=weather$TIME, rain=ifelse(weather$RAIN == 0, 0, 1))
plot(rain$date, rain$rain, pch=16)
summary(rain)

rain_duration <- c()
mins_rain <- 0

for (i in 1:length(rain$date)) {
  if (rain$rain[i] == 1) {
    mins_rain <- mins_rain + 5
  } else {
    if (mins_rain != 0) {
      rain_duration <- c(rain_duration, mins_rain)
      mins_rain <- 0
    }
  }
}

rain_duration
hist(rain_duration)
summary(rain_duration)
```

## Including Plots

You can also embed plots, for example:
28/99 make U, 71 don't
25th card made U
```{r pressure, echo=FALSE}
71/99
chances <- c()
chance <- 1
for (i in c(1:24)){
  chance <- chance * ((72-i)/(100-i))
  print(chance)
  chances <- c(chances, chance)
}
plot(chances)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
